Development of Performance Regression Analysis Tool using Distributed Tracing on Microservice-based Application\\

### 2022-06-23 paper.tex
txs auto checkin

The paper is organized as follows. Section II presents related
work in the area of performance regression and distributed tracing. Section III discusses problem analysis, the design and the underlying architecture, and the implementation of the PRA system. Section IV shows the experiments done with the PRA system. Section V discusses a few analysis from the experiments done in Section V. Section
VI concludes the work.

\section{Related Works}

@@

>>>>

The paper is organized as follows. Section II presents related
work in the area of performance regression. Section III discusses problem analysis, the design and the underlying architecture, and the implementation of the PRA system. Section IV shows the experiments done with the PRA system. Section V discusses a few analysis from the experiments done in Section V. Section
VI concludes the work.

\section{Related Works}
This section will discuss two related works that inspired this paper.

@@

In the future, a similar system can be implemented to analyze performance regression outside of Kubernetes environment.
